Fourmile Calibrations

### 2022-12-29 calibration_output.Rmd
new model results using outlet only

```{r hydrographs, echo = F}
# flow <- read_csv('discharge_all.csv') %>%
#   replace(.==-9999, NA)
# 
# 
# flow_pivot <- flow %>%
#   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
#   mutate(WY = as.factor(calcWaterYear(date)))
#   
# 
# q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
#   geom_line()
# 
# ggplotly(q)

@@

### Hydrograph by WY

@@

# plotq_wy <- function(wateryear) {
#   {flow_pivot %>%
#     filter(WY == wateryear) %>%
#     ggplot(aes(x = date,
#                y = q_m3s,
#                color = cal_run)) + 
#     geom_line() + 
#     ggtitle(wateryear) +
#     theme_bw()} %>%
#     ggplotly()
#   
# }
# 
# name <- levels(flow_pivot$WY)
# 
# try <- lapply(name, plotq_wy)
# 
# htmltools::tagList(try)

@@

# flow_kge_all <- flow %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)
# 
# flow_kge_all <- flow_kge_all %>%
#   pivot_longer(everything()) %>%
#   arrange(value)
# 
# kable(flow_kge_all) %>%
#   kable_styling(full_width = F)

@@

### Model run KGE by water year (outlet)

@@

# flow_year <- flow %>%
#   mutate(WY = calcWaterYear(date)) %>%
#   group_by(WY) %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)
# 
# flow_kge <- flow_year %>%
#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
#   pivot_wider(names_from = 'WY', values_from = 'kge')
# 
# flow_kge %>%
#   kable(.) %>%
#   kable_styling()
# 
# 
# flow_plot <- flow_year %>%
#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
#   mutate(WY = as.factor(WY))
# 
# 
# kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
#   theme_bw()
# 
# ggplotly(kge_plot_wy)

@@

### Model run KGE plots by water year

@@

# plot_kge <- function(wateryear) {
#   flow_plot %>%
#     filter(WY == wateryear) %>%
#     ggplot(aes(x = model_run,
#                y = kge)) + 
#     geom_col() + 
#     ggtitle(wateryear) +
#     theme_bw() +
#     theme(axis.text.x = element_text(angle = 45, hjust=1))
# }
# 
# name <- levels(flow_plot$WY)
# 
# lapply(name, plot_kge)

@@

## Reach results

### Hydrograph by reach

>>>>

```{r hydrographs, echo = F}
flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(year = as.factor(year(date)))

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line()

ggplotly(q)

@@

### Hydrograph by calendar year

@@

plotq_cy <- function(calyear) {
  {flow_pivot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = q_m3s,
               color = cal_run)) +
    geom_line() +
    ggtitle(calyear) +
    theme_bw()} %>%
    ggplotly()

}

name <- levels(flow_pivot$year)

try <- lapply(name, plotq_cy)

htmltools::tagList(try)

#try

@@

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling(full_width = F)

@@

### Model run KGE by calendar year (outlet)

@@

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'year', values_from = 'kge')

flow_kge %>%
  kable(.) %>%
  kable_styling()

flow_plot <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  mutate(year = as.factor(year))

kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) + geom_point(size = 3) +
  theme_bw()

ggplotly(kge_plot_cy)

@@

### Model run KGE plots by calendar year

@@

plot_kge <- function(calyear) {
  flow_plot %>%
    filter(year == calyear) %>%
    ggplot(aes(x = model_run,
               y = kge)) +
    geom_col() +
    ggtitle(calyear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(flow_plot$year)

lapply(name, plot_kge)

@@
